---
title: "Paper: Inequality Belief Systems and Attitude Towards Redistribution in US and the Netherlands"
author: ""
#date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    fig_caption: yes
    df_print: paged
---

<style>
body {
text-align: justify}
</style>

```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r include=FALSE}
library(pacman)
p_load(tidyverse, here, stargazer, sjmisc, texreg, sjPlot, jtools, kableExtra,
       poLCA, corclass, EGAnet, sjlabelled, haven, conflicted, imager)
```


```{r}
#Data
load(here("Output",  "230314 - Output.RData"))

#Pvalues
load(here("Output",  "230314 - pvalues.RData"))

```

```{r}
mijs_us = mijs_us %>% 
  mutate(CCA = ifelse(CCA=="3", "0", "1"))

mijs_nl = mijs_nl %>% 
  mutate(CCA = ifelse(CCA=="3", "1", "0"))

frq(mijs_us, CCA)
frq(mijs_nl, CCA)

  
```



```{r}
#Packages conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("texreg", "extract")
conflict_prefer("sjlabelled", "get_label")
#conflict_prefer("labelled", "to_character")



options(max.print=999999)
options(scipen=999999)
```

# Variables

```{r}
labels_data = sjlabelled::get_label(mijs_us) %>%
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  `colnames<-`(c("variable", "label")) %>% 
  slice(17:34)

labels_data %>% 
  kable()
  
```


# Descriptives

## US

```{r}
#US
mijs_us_skim  = mijs_us %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

## NL

```{r}
#NL
mijs_nl_skim  = mijs_nl %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

# T-tests

## US

```{r}
frq(mijs_us, treatment)
```

```{r}
pvalues_us01 = pvalues_us01 %>% mutate(group1 = "Control", group2 = "Wealth inequality")
pvalues_us02 = pvalues_us02 %>% mutate(group1 = "Control", group2 = "Racial discrimination")
pvalues_us03 = pvalues_us03 %>% mutate(group1 = "Control", group2 = "Coronavirus")
pvalues_us12 = pvalues_us12 %>% mutate(group1 = "Wealth inequality", group2 = "Racial discrimination")
pvalues_us13 = pvalues_us13 %>% mutate(group1 = "Wealth inequality", group2 = "Coronavirus")
pvalues_us23 = pvalues_us23 %>% mutate(group1 = "Racial discrimination", group2 = "Coronavirus")

pvalues_us01 %>% 
  bind_rows(pvalues_us02) %>% 
  bind_rows(pvalues_us03) %>% 
  bind_rows(pvalues_us12) %>% 
  bind_rows(pvalues_us13) %>% 
  bind_rows(pvalues_us23) %>% 
  select(group1, group2, variable, dif_mean, pvalues)
```

## NL

```{r}
frq(mijs_nl, treatment)
```

```{r}
pvalues_nl01 = pvalues_nl01 %>% mutate(group1 = "Control", group2 = "Wealth inequality")
pvalues_nl02 = pvalues_nl02 %>% mutate(group1 = "Control", group2 = "Racial discrimination")
pvalues_nl12 = pvalues_nl12 %>% mutate(group1 = "Wealth inequality", group2 = "Racial discrimination")

pvalues_nl01 %>% 
  bind_rows(pvalues_nl02) %>% 
  bind_rows(pvalues_nl12) %>% 
  select(group1, group2, variable, dif_mean, pvalues)
```

# Inequality Belief Systems

## CCA

### US

```{r}
CCA_group_US
plot(CCA_group_US, 1)
plot(CCA_group_US, 3)
```

### NL

```{r}
CCA_group_NL
plot(CCA_group_NL, 1)
plot(CCA_group_NL, 3)
```

## LCA

### US

```{r}
US7_jpeg = imager::load.image(here("Output",  "7US.jpeg"))

plot(US7_jpeg, axes=FALSE)
```

[High resolution image](https://drive.google.com/file/d/1jMVEYzYwxZVQYososHPFhkJYOFIMPfoY/view?usp=share_link)

### NL

```{r}
NL6_jpeg = imager::load.image(here("Output",  "6NL.jpeg"))

plot(NL6_jpeg, axes=FALSE)
```

[High resolution image](https://drive.google.com/file/d/1ULvndzTUvA-81y28DsDmjdRDuWUMSMIS/view?usp=share_link)

##Summary CCA and LCA

### US

```{r}
frq(mijs_us, CCA, LCA)
```

### NL

```{r}
frq(mijs_nl, CCA, LCA)
```

## EGA (CCA)

### US

#### Group 1
```{r}
plot(US_ega_CCA1)
```

#### Group 3
```{r}
plot(US_ega_CCA2)
```

### NL

#### Group 1

```{r}
plot(NL_ega_CCA1)
```

#### Group 3
```{r}
plot(NL_ega_CCA2)
```

# Inequality Belief Systems and Attitude Towards Redistribution

## Graphs

### US

```{r}
#graph
mijs_us_n = nrow(mijs_us)

crosstab_US = mijs_us %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_US.jpg"), plot =  crosstab_US)

crosstab_US
```

### NL

```{r}
#graph
mijs_nl_n = nrow(mijs_nl)

crosstab_NL = mijs_nl %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_NL.jpg"), plot =  crosstab_NL)

crosstab_NL

```

## Regressions

### US

```{r}
#regression
mijs_us = mijs_us %>% 
  mutate(CCA = as.factor(paste0(CCA)),
         hhincome = as.factor(paste0(hhincome)))

mijs_us = mijs_us %>% 
  mutate(treatment = as.factor(treatment))

m1_US = lm(att_redist ~ CCA, data = mijs_us)
m2_US = lm(att_redist ~ CCA + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)
m3_US = lm(att_redist ~ age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)

#Treatment

m1_US_t = lm(att_redist ~ CCA + treatment, data = mijs_us)
m2_US_t = lm(att_redist ~ CCA + treatment + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)
m3_US_t = lm(att_redist ~ treatment + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)


#xtable
screenreg(list(m1_US, m2_US, m3_US, m1_US_t, m2_US_t, m3_US_t), stars = c(0.01,0.05,0.1))
```

### NL

```{r}
#regression
mijs_nl = mijs_nl %>% 
  mutate(CCA = as.factor(paste0(CCA)),
         hhincome = as.factor(paste0(hhincome)))

mijs_nl = mijs_nl %>% 
  mutate(treatment = as.factor(treatment))

m1_NL = lm(att_redist ~ CCA, data = mijs_nl)
m2_NL = lm(att_redist ~ CCA + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)
m3_NL = lm(att_redist ~ age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)

#Treatment

m1_NL_t = lm(att_redist ~ CCA + treatment, data = mijs_nl)
m2_NL_t = lm(att_redist ~ CCA + treatment + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)
m3_NL_t = lm(att_redist ~ treatment + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)


#xtable
screenreg(list(m1_NL, m2_NL, m3_NL, m1_NL_t, m2_NL_t, m3_NL_t), stars = c(0.01,0.05,0.1))
```


# Sociodemographic determinants of inequality belief systems


## Regressions

### US

```{r}

mijs_us = mijs_us %>% 
  re

#regression
m1_US = lm(att_redist ~ CCA, data = mijs_us)
m2_US = lm(att_redist ~ CCA + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)
m3_US = lm(att_redist ~ age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_us)

#xtable
screenreg(list(m1_US, m2_US, m3_US), stars = c(0.01,0.05,0.1))
```

### NL

```{r}
#regression
m1_NL = lm(att_redist ~ CCA, data = mijs_nl)
m2_NL = lm(att_redist ~ CCA + age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)
m3_NL = lm(att_redist ~ age + sex + race + education + working + politics + 
        hhincome + immigrant + marital + religion, data = mijs_nl)

#xtable
screenreg(list(m1_NL, m2_NL, m3_NL), stars = c(0.01,0.05,0.1))
```

# Pendant

## Recode of control variables

### US

```{r}
frq(mijs_us, age, sex, race, education, working, politics, immigrant, marital, religion, peducation)
```


### NL

```{r}
frq(mijs_us, age, sex, race, education, working, politics, immigrant, marital, religion)
frq(mijs_nl, age, sex, race, education, working, politics, immigrant, marital, religion)

```
