---
title: "Paper: Inequality Belief Systems and Attitude Towards Redistribution in US and the Netherlands"
author: ""
#date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    fig_caption: yes
    df_print: paged
---

<style>
body {
text-align: justify}
</style>

```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r include=FALSE}
library(pacman)
p_load(tidyverse, here, stargazer, sjmisc, texreg, sjPlot, jtools, kableExtra,
       poLCA, corclass, EGAnet, sjlabelled, haven, conflicted, imager)
```


```{r}
#Data
load(here("Output",  "230314 - Output.RData"))

#Pvalues
load(here("Output",  "230314 - pvalues.RData"))

```


```{r}
#Packages conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("texreg", "extract")
conflict_prefer("sjlabelled", "get_label")
#conflict_prefer("labelled", "to_character")



options(max.print=999999)
options(scipen=999999)
```

# Variables

```{r}
mijs_us = mijs_us %>% 
  mutate(CCA = as.numeric(paste0(CCA)))

mijs_nl = mijs_nl %>% 
  mutate(CCA = as.numeric(paste0(CCA)))

```

```{r}
labels_data = sjlabelled::get_label(mijs_us) %>%
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  `colnames<-`(c("variable", "label")) %>% 
  slice(19:35)

labels_data %>% 
  kable()
  
```


## Descriptives

### US

```{r}
#US
mijs_us_skim  = mijs_us %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

### NL

```{r}
#NL
mijs_nl_skim  = mijs_nl %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

# Inequality Belief Systems

## Distribution

### US

```{r}
frq(mijs_us, CCA)
```

### NL

```{r}
frq(mijs_nl, CCA)
```

## EGA

### US

#### Group 0

```{r}
plot(US_ega_CCA2)
```

#### Group 1

```{r}
plot(US_ega_CCA1)
```

### NL

#### Group 0

```{r}
plot(NL_ega_CCA1)
```

#### Group 1
```{r}
plot(NL_ega_CCA2)
```

# Sociodemographic Determinants of Inequality Belief Systems

## Regressions

```{r}

# frq(mijs_us, age, agegroups, sex, race, education,
#          working, politics, pol5, 
#          hhincome, hhincome_groups, assets, immigrant, marital, religion, ladder_present)

#regression
m1_US_d = glm(CCA ~ assets, data = mijs_us, family=binomial(link="logit"))
m2_US_d = glm(CCA ~ assets + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us, family=binomial(link="logit"))
m3_US_d = glm(CCA ~ agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us, family=binomial(link="logit"))

#xtable
#screenreg(list(m1_US_d, m2_US_d, m3_US_d), stars = c(0.01,0.05,0.1))
# tab_model(list(m1_US_d, m2_US_d, m3_US_d),
#           show.p = TRUE,
#           p.style = "stars",
#           p.threshold = c(0.1, 0.05, 0.01),
#           dv.labels = c("M1", "M2", "M3"),
#           collapse.ci = TRUE,
#           show.aic = TRUE,
#           #show.reflvl = TRUE,
#           title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - US",
#             string.pred = " "
# )
```

```{r}
#regression
m1_NL_d = glm(CCA ~ assets, data = mijs_nl, family=binomial(link="logit"))
m2_NL_d = glm(CCA ~ assets + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl, family=binomial(link="logit"))
m3_NL_d = glm(CCA ~ agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl, family=binomial(link="logit"))

#xtable
#screenreg(list(m1_NL_d, m2_NL_d, m3_NL_d), stars = c(0.01,0.05,0.1))
# tab_model(list(m1_NL_d, m2_NL_d, m3_NL_d),
#           show.p = TRUE,
#           p.style = "stars",
#           p.threshold = c(0.1, 0.05, 0.01),
#           dv.labels = c("M1", "M2", "M3"),
#           collapse.ci = TRUE,
#           show.aic = TRUE,
#           #show.reflvl = TRUE,
#           title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - NL",
#             string.pred = " "
# )
```

```{r}
tab_model(list(m1_US_d, m2_US_d, m3_US_d, m1_NL_d, m2_NL_d, m3_NL_d),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1_US", "M2_US", "M3_US", "M1_NL", "M2_NL", "M3_NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - US & NL",
            string.pred = " "
)
```

# Inequality Belief Systems and Attitude Towards Redistribution

## Graphs

### US

```{r}
#graph
mijs_us_n = nrow(mijs_us)

crosstab_US = mijs_us %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_US.jpg"), plot =  crosstab_US)

crosstab_US
```

### NL

```{r}
#graph
mijs_nl_n = nrow(mijs_nl)

crosstab_NL = mijs_nl %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_NL.jpg"), plot =  crosstab_NL)

crosstab_NL

```

## Regressions


```{r}
#regression
mijs_us = mijs_us %>% 
  mutate(CCA = as.factor(paste0(CCA)),
         hhincome = as.factor(paste0(hhincome)))

mijs_us = mijs_us %>% 
  mutate(treatment = as.factor(treatment))

m1_US = lm(att_redist ~ CCA, data = mijs_us)
m2_US = lm(att_redist ~ CCA + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us)
m3_US = lm(att_redist ~ agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us)

#Treatment

m1_US_t = lm(att_redist ~ CCA + treatment, data = mijs_us)
m2_US_t = lm(att_redist ~ CCA + treatment + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us)
m3_US_t = lm(att_redist ~ treatment + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us)


#xtable
#screenreg(list(m1_US, m2_US, m3_US, m1_US_t, m2_US_t, m3_US_t), stars = c(0.01,0.05,0.1))
```

```{r}
#regression
mijs_nl = mijs_nl %>% 
  mutate(CCA = as.factor(paste0(CCA)),
         hhincome = as.factor(paste0(hhincome)))

mijs_nl = mijs_nl %>% 
  mutate(treatment = as.factor(treatment))

m1_NL = lm(att_redist ~ CCA, data = mijs_nl)
m2_NL = lm(att_redist ~ CCA + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl)
m3_NL = lm(att_redist ~ agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl)

#Treatment

m1_NL_t = lm(att_redist ~ CCA + treatment, data = mijs_nl)
m2_NL_t = lm(att_redist ~ CCA + treatment + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl)
m3_NL_t = lm(att_redist ~ treatment + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl)


#xtable
#screenreg(list(m1_NL, m2_NL, m3_NL, m1_NL_t, m2_NL_t, m3_NL_t), stars = c(0.01,0.05,0.1))
```

### Without Treatment Control

```{r}
tab_model(list(m1_US, m2_US, m3_US, m1_NL, m2_NL, m3_NL),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1_US", "M2_US", "M3_US", "M1_NL", "M2_NL", "M3_NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on preference for redistribution - US & NL (Without Treatment)",
            string.pred = " "
)
```

### With Treatment Control

```{r}
tab_model(list(m1_US_t, m2_US_t, m3_US_t, m1_NL_t, m2_NL_t, m3_NL_t),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1_US", "M2_US", "M3_US", "M1_NL", "M2_NL", "M3_NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on preference for redistribution - US & NL (With Treatment)",
            string.pred = " "
)
```


# Robustness check (Treatment groups)

## T-tests

### US

```{r}
frq(mijs_us, treatment)
```

```{r}
pvalues_us01 = pvalues_us01 %>% mutate(group1 = "Control", group2 = "Wealth inequality")
pvalues_us02 = pvalues_us02 %>% mutate(group1 = "Control", group2 = "Racial discrimination")
pvalues_us03 = pvalues_us03 %>% mutate(group1 = "Control", group2 = "Coronavirus")
pvalues_us12 = pvalues_us12 %>% mutate(group1 = "Wealth inequality", group2 = "Racial discrimination")
pvalues_us13 = pvalues_us13 %>% mutate(group1 = "Wealth inequality", group2 = "Coronavirus")
pvalues_us23 = pvalues_us23 %>% mutate(group1 = "Racial discrimination", group2 = "Coronavirus")

pvalues_us01 %>% 
  bind_rows(pvalues_us02) %>% 
  bind_rows(pvalues_us03) %>% 
  bind_rows(pvalues_us12) %>% 
  bind_rows(pvalues_us13) %>% 
  bind_rows(pvalues_us23) %>% 
  select(group1, group2, variable, dif_mean, pvalues)
```

### NL

```{r}
frq(mijs_nl, treatment)
```

```{r}
pvalues_nl01 = pvalues_nl01 %>% mutate(group1 = "Control", group2 = "Wealth inequality")
pvalues_nl02 = pvalues_nl02 %>% mutate(group1 = "Control", group2 = "Racial discrimination")
pvalues_nl12 = pvalues_nl12 %>% mutate(group1 = "Wealth inequality", group2 = "Racial discrimination")

pvalues_nl01 %>% 
  bind_rows(pvalues_nl02) %>% 
  bind_rows(pvalues_nl12) %>% 
  select(group1, group2, variable, dif_mean, pvalues)
```


## EGA (Treatment group 1 - Wealth inequality)

### US

```{r}
plot(US_ega_CCA1_control)
plot(US_ega_CCA2_control)
```

### NL

```{r}
plot(NL_ega_CCA1_control)
plot(NL_ega_CCA2_control)
```

