---
title: "Design 1: Inequality Belief Systems and Attitude Towards Redistribution in US and the Netherlands"
author: ""
#date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    fig_caption: yes
    df_print: paged
---

<style>
body {
text-align: justify}
</style>

```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo = FALSE,
	fig.align="center",
	out.width='\\textwidth'
	)
```


# Input

```{r message=FALSE, warning=FALSE}
library(pacman)
p_load(tidyverse, janitor, here, haven, labelled, sjmisc, skimr, ggplot2, jtools,
       stargazer, qgraph, Matrix, igraph, NetworkComparisonTest, bootnet,
       rio, foreign, matrixcalc, corclass, NetworkComparisonTest, conflicted, 
       EGAnet, texreg, ggpubr, lavaan, ltm, kableExtra, sjPlot, psych, nFactors)

```

```{r}
#Packages conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("igraph", "compose")


options(max.print=999999)
options(scipen=999)
```


```{r}

#Load
rm(list = ls())
load(here("Output",  "230515 - Data_Databases.RData"))

```

```{r}
labels_data = sjlabelled::get_label(data_us) %>%
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  `colnames<-`(c("variable", "label")) %>% 
  slice(19:35)

labels_data %>% 
  kable()
  
```


# Processing

## Descriptives

### US

```{r}

data_us_skim  = data_us %>% 
  select(starts_with("p_"),
         starts_with("b_"),
         starts_with("ib_"),
         starts_with("att_"),
agegroups, sex, race, education, working, assets, 
        hhincome_groups, immigrant, marital, religion) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

### NL

```{r}

data_nl_skim  = data_nl %>% 
  select(starts_with("p_"),
         starts_with("b_"),
         starts_with("ib_"),
         starts_with("att_"),
agegroups, sex, race, education, working, assets, 
        hhincome_groups, immigrant, marital, religion) %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")

```


## CCA

### US

```{r}

#CCA applied to ISSP US
cca_group_us <- cca(data_us_cca, filter.significance = TRUE, filter.value = 0.01, 
                 zero.action = c("ownclass"))  

#Preliminary plots
us_plot_cca_1 = plot(cca_group_us, 1)
us_plot_cca_3 = plot(cca_group_us, 3)

```

```{r}
#Add membership to US
data_us_cca$cca = cca_group_us$membership
data_us$cca = cca_group_us$membership

#Prepare CCA-driven dataframe for EGA
cca_us_1 = data_us_cca %>% 
  as.data.frame() %>% 
  filter(cca == 1) %>%
  select(p_income:ib_sex)

cca_us_0 = data_us_cca %>% 
  as.data.frame() %>% 
  filter(cca == 3) %>%
  select(p_income:ib_sex)

#Filter out second CCA class
data_us_cca = data_us_cca %>% 
  filter(cca != 2)
```


```{r echo=TRUE}
#Rename CCA groups
data_us = data_us %>% 
  mutate(cca = ifelse(cca=="3", 0, 1))

data_us_cca = data_us_cca %>% 
  mutate(cca = ifelse(cca=="3", 0, 1))

```

### NL

```{r}

#CCA applied to ISSP NL
cca_group_nl <- cca(data_nl_cca, filter.significance = TRUE, filter.value = 0.01, 
                 zero.action = c("ownclass"))  

#Preliminary plots
nl_plot_cca_1 = plot(cca_group_nl, 1)
nl_plot_cca_3 = plot(cca_group_nl, 3)

```

```{r}
#Add membership to NL
data_nl_cca$cca = cca_group_nl$membership
data_nl$cca = cca_group_nl$membership

#Prepare CCA-driven dataframe for EGA
cca_nl_1 = data_nl_cca %>% 
  as.data.frame() %>% 
  filter(cca == 1) %>%
  select(p_income:ib_sex)

cca_nl_0 = data_nl_cca %>% 
  as.data.frame() %>% 
  filter(cca == 3) %>%
  select(p_income:ib_sex)

#Filter out second CCA class
data_nl_cca = data_nl_cca %>% 
  filter(cca != 2)
```


```{r echo=TRUE}
#Rename CCA groups

data_nl = data_nl %>% 
  mutate(cca = ifelse(cca=="3", 1, 0))

data_nl_cca = data_nl_cca %>% 
  mutate(cca = ifelse(cca=="3", 1, 0))

```


## EGA

### US

```{r include=FALSE}
#EGA databases
us_cca0_ega = data_us_cca %>% 
  filter(cca == 0) %>%
  select(p_income:ib_sex)

us_cca1_ega = data_us_cca %>% 
  filter(cca == 1) %>%
  select(p_income:ib_sex)


#EGA
ega_us0 <- EGA(data=us_cca0_ega,  model = "glasso", 
                  plot.EGA = TRUE, 
                  plot.args = list(
                    plot.type = "qgraph",
                    vsize = 15, 
                    alpha = 0.8,
                    legend.position = "none", legend.size = NA,
                    edge.color = c("royalblue", "tomato")))

ega_us1 <- EGA(data=us_cca1_ega,  model = "glasso", 
                  plot.EGA = TRUE, 
                  plot.args = list(
                    plot.type = "qgraph",
                    vsize = 15, 
                    alpha = 0.8,
                    legend.position = "none", legend.size = NA,
                    edge.color = c("royalblue", "tomato")))
```

### NL

```{r include=FALSE}
#EGA databases
nl_cca0_ega = data_nl_cca %>% 
  filter(cca == 0) %>%
  select(p_income:ib_sex)

nl_cca1_ega = data_nl_cca %>% 
  filter(cca == 1) %>%
  select(p_income:ib_sex)

#EGA
ega_nl0 <- EGA(data=nl_cca0_ega,  model = "glasso", 
                  plot.EGA = TRUE, 
                  plot.args = list(
                    plot.type = "qgraph",
                    vsize = 15, 
                    alpha = 0.8,
                    legend.position = "none", legend.size = NA,
                    edge.color = c("royalblue", "tomato")))

ega_nl1 <- EGA(data=nl_cca1_ega,  model = "glasso", 
                  plot.EGA = TRUE, 
                  plot.args = list(
                    plot.type = "qgraph",
                    vsize = 15, 
                    alpha = 0.8,
                    legend.position = "none", legend.size = NA,
                    edge.color = c("royalblue", "tomato")))
```

### Plots

```{r include=FALSE}
#EGA list
list_data_egas <- lapply(ls(pattern="^ega_"), function(x) get(x))
list_data_egas <- list_data_egas[c(3,4,1,2)]
cca_groups = c("US_0", "US_1", "NL_0", "NL_1")

#Compare EGAs
comp_egas = compare.EGA.plots(
  input.list = list_data_egas,
  base.plot = 1,
  labels = cca_groups,
  rows = 2, columns = 2,
  plot.args = list(
    plot.type = "qgraph",
    vsize = 15, 
    alpha = 0.8,
    legend.position = "none", legend.size = NA,
    edge.color = c("royalblue", "tomato"),
    plot.margin = margin(6,6,6,6, "mm")))

#Individual plots
plot_ega_us_0 = comp_egas$individual.plots$`US_0` +
      ggtitle("US 0") +
      theme(plot.title = element_text(size=20, face="bold", hjust = 0.5),
            plot.margin = margin(2,2,2,2, "mm"))

ggsave(here("Output", "Supplemental", "ega_us0.jpg"), 
       plot_ega_us_0, height = 6, width = 6)

plot_ega_us_1 = comp_egas$individual.plots$`US_1` +
      ggtitle("US 1") +
      theme(plot.title = element_text(size=20, face="bold", hjust = 0.5),
            plot.margin = margin(2,2,2,2, "mm"))

ggsave(here("Output", "Supplemental", "ega_us1.jpg"), 
       plot_ega_us_1, height = 6, width = 6)

plot_ega_nl_0 = comp_egas$individual.plots$`NL_0` +
      ggtitle("NL 0") +
      theme(plot.title = element_text(size=20, face="bold", hjust = 0.5),
            plot.margin = margin(2,2,2,2, "mm"))

ggsave(here("Output", "Supplemental", "ega_nl0.jpg"), 
       plot_ega_nl_0, height = 6, width = 6)

plot_ega_nl_1 = comp_egas$individual.plots$`NL_1` +
      ggtitle("NL 1") +
      theme(plot.title = element_text(size=20, face="bold", hjust = 0.5),
            plot.margin = margin(2,2,2,2, "mm"))

ggsave(here("Output", "Supplemental", "ega_nl1.jpg"), 
       plot_ega_nl_1, height = 6, width = 6)


#Full plot
comp_egas_full = comp_egas$comparison.plot

plot_egas <- lapply(ls(pattern="^plot_ega_"), function(x) get(x))
plot_egas <- plot_egas[c(3,4,1,2)]

g_plot_egas = ggarrange(plotlist = plot_egas, ncol = 2, nrow = 2) 


#Save
ggsave(here("Output", "Article", "Graphs", "ega_full.jpg"), 
       g_plot_egas, height = 12, width = 12)

```

```{r}
plot_ega_us_0
plot_ega_us_1
plot_ega_nl_0
plot_ega_nl_1
```



### NCT

```{r include=FALSE}

#US
set.seed(1)
nct_us = NCT(cca_us_0, cca_us_1, 
    gamma = 0.5, test.edges = TRUE, edges = "all", 
    test.centrality = TRUE, centrality = "strength")

inputNCTgraph <- ega_us0$network - ega_us1$network
inputNCTgraph[upper.tri(inputNCTgraph)][which(nct_us$einv.pvals$`p-value` >= .05)] <- 0
inputNCTgraph <- forceSymmetric(inputNCTgraph)

nct_us_plot = qgraph(inputNCTgraph, 
       #layout = "spring", 
       edge.labels = TRUE)


pdf(here("Output", "Supplemental", "nct_us.pdf"))
nct_us_plot
dev.off()

#NL
set.seed(1)
nct_nl = NCT(cca_nl_0, cca_nl_1, 
    gamma = 0.5, test.edges = TRUE, edges = "all", 
    test.centrality = TRUE, centrality = "strength")

inputNCTgraph <- ega_nl0$network - ega_nl1$network
inputNCTgraph[upper.tri(inputNCTgraph)][which(nct_nl$einv.pvals$`p-value` >= .05)] <- 0
inputNCTgraph <- forceSymmetric(inputNCTgraph)

nct_nl_plot = qgraph(inputNCTgraph, 
       #layout = "spring", 
       edge.labels = TRUE)

pdf(here("Output", "Supplemental", "nct_nl.pdf"))
nct_nl_plot
dev.off()

```
#### US

```{r}
plot(nct_us_plot)
```

#### NL

```{r}
plot(nct_nl_plot)
```

## Sociodemographic Determinants of Inequality Belief Systems

### US

```{r}
#Regressions
m1_us = glm(cca ~ politics, data = data_us, family=binomial(link="logit"))
m2_us = glm(cca ~ politics + agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = data_us, family=binomial(link="logit"))
m3_us = glm(cca ~ agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = data_us, family=binomial(link="logit"))
```

### NL

```{r}
#Regressions
m1_nl = glm(cca ~ politics, data = data_nl, family=binomial(link="logit"))
m2_nl = glm(cca ~ politics + agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = data_nl, family=binomial(link="logit"))
m3_nl = glm(cca ~ agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = data_nl, family=binomial(link="logit"))
```


```{r}

#Output
tab_model(list(m1_us, m2_us, m3_us, m1_nl, m2_nl, m3_nl),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1-US", "M2-US", "M3-US", "M1-NL", "M2-NL", "M3-NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Logistic regression models on inequality belief membership - US & NL",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Article", "Tables", "Sociodemographic_Determinants.html")
)

```



## Inequality Belief Systems and Attitude Towards Redistribution

### Graphs

#### US

```{r include=FALSE}

#cross tab
data_us %>%
  select(cca, att_redist) %>%
  flat_table(margin = "row", digits = 1)

#graph
data_us_n = nrow(data_us)

crosstab_us = data_us %>%
  group_by(cca) %>% 
  mutate(n_cca = n()) %>%
  group_by(cca, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~cca) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "Article", "Graphs", "Bar_Graph_Att_Redistribution_US.jpg"), plot =  crosstab_us)
```

```{r}
crosstab_us
```


#### NL

```{r include=FALSE}

#cross tab
data_nl %>%
  select(cca, att_redist) %>%
  flat_table(margin = "row", digits = 1)

#graph
data_nl_n = nrow(data_nl)

crosstab_nl = data_nl %>%
  group_by(cca) %>% 
  mutate(n_cca = n()) %>%
  group_by(cca, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~cca) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "Article", "Graphs", "Bar_Graph_Att_Redistribution_NL.jpg"), plot =  crosstab_nl)
```

```{r}
crosstab_nl
```


### Regressions

We have different ways to do the final regression (cca variable + predictors -> att_redis). 

#### Design A: Based on EGA communities

First solution: We fit EGA on the full samples US and NL; we create  means indexes starting from EGA groups; we do this because we rely on this: "we can state the following relationship as a fundamental rule of network psychometrics: Clusters in network = latent variables." [Paper link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0174035).  However, here we have a problem, since these indexes have poor Cronbach alpha, and if we try to fit this structure with a CFA we have poor fit too. Therefore if we go on with this route we can say we are estimating mean indexes of each community, but it is hard to state we are building mean indexes of latent factor. Still, if we take this route we have the best regression results (CCA variable significant, increase in R2, only for NL)

##### EGA by country

```{r include=FALSE}
#EGA US
data_us_net = data_us %>% 
  select(p_income:ib_sex)

US_ega = EGA(data=data_us_net,  model = "glasso", 
                  plot.EGA = TRUE) 

#EGA NL
data_nl_net = data_nl %>% 
  select(p_income:ib_sex)

NL_ega = EGA(data=data_nl_net,  model = "glasso", 
                  plot.EGA = TRUE) 

#CFA
data_cfa_us = CFA(US_ega, data_us_net, estimator = "WLSMV")
data_cfa_nl = CFA(NL_ega, data_nl_net, estimator = "WLSMV")


#Indexes
data_us = data_us %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, p_poor, p_black, b_diversity, b_equality))),
           index_2 = rowMeans(across(c(b_merit, ib_weafam, ib_edu, ib_edupar, ib_work, ib_people))),
           index_3 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))


data_nl = data_nl %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, p_poor, p_black, b_merit, b_diversity, b_equality))),
           index_2 = rowMeans(across(c(ib_weafam, ib_edu, ib_edupar, ib_work, ib_people))),
           index_3 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))

#Databases us
index_1_us = data_us %>% 
  select(p_income, p_wealth, p_poor, p_black, b_diversity, b_equality)

index_2_us = data_us %>% 
  select(b_merit, ib_weafam, ib_edu, ib_edupar, ib_work, ib_people)

index_3_us = data_us %>% 
  select(ib_race, ib_migra, ib_relig, ib_sex)

#Databases nl
index_1_nl = data_us %>% 
  select(p_income, p_wealth, p_poor, p_black, b_merit, b_diversity, b_equality)

index_2_nl = data_us %>% 
  select(ib_weafam, ib_edu, ib_edupar, ib_work, ib_people)

index_3_nl = data_us %>% 
  select(ib_race, ib_migra, ib_relig, ib_sex)
```

##### Indexes


```{r echo=TRUE}

#Indexes
data_us = data_us %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, p_poor, p_black, b_diversity, b_equality))),
           index_2 = rowMeans(across(c(b_merit, ib_weafam, ib_edu, ib_edupar, ib_work, ib_people))),
           index_3 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))


data_nl = data_nl %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, p_poor, p_black, b_merit, b_diversity, b_equality))),
           index_2 = rowMeans(across(c(ib_weafam, ib_edu, ib_edupar, ib_work, ib_people))),
           index_3 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))

#Cronbach
cronbach.alpha(index_1_us, CI=TRUE, standardized=TRUE) # 0.858
cronbach.alpha(index_2_us, CI=TRUE, standardized=TRUE) # 0.456
cronbach.alpha(index_3_us, CI=TRUE, standardized=TRUE) # 0.735

cronbach.alpha(index_1_nl, CI=TRUE, standardized=TRUE) # 0.761
cronbach.alpha(index_2_nl, CI=TRUE, standardized=TRUE) # 0.512
cronbach.alpha(index_3_nl, CI=TRUE, standardized=TRUE) # 0.735

```

##### Regressions

```{r}

#US
m0_us = lm(att_redist ~ cca, data = data_us)
m1_us = lm(att_redist ~ index_1 + index_2 + index_3, data = data_us)
m2_us = lm(att_redist ~ index_1 + index_2 + index_3 + cca, data = data_us)
m3_us = lm(att_redist ~ index_1 + index_2 + index_3 + cca + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_us)

#NL
m0_nl = lm(att_redist ~ cca, data = data_nl)
m1_nl = lm(att_redist ~ index_1 + index_2 + index_3, data = data_nl)
m2_nl = lm(att_redist ~ index_1 + index_2 + index_3 + cca, data = data_nl)
m3_nl = lm(att_redist ~ index_1 + index_2 + index_3 + cca + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_nl)
```


```{r}

#Output
tab_model(list(m0_us, m1_us, m2_us, m3_us, m0_nl, m1_nl, m2_nl, m3_nl),
          #order.terms = c(1:5, 23, 6:22),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1-US", "M2-US", "M3-US", "M4-US", "M1-NL", "M2-NL", "M3-NL", "M4-NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on attitude towards redistribution - US & NL",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Article", "Tables", "Attitude_Redistribution_A.html")
)

```


#### Design B: Based on EFA factors

Second route: since EGA did not retrieve a decent data structure (poor alpha, poor fit) we can do two factor analysis, one in NL one in US. If we do this we end up with a set of indexes. Later, we can put all these indexes and variables in the regression. Results say we have a significant effect of the CCA variable and an increase in the R2, but only for NL. Additionally, Cronbach alphas still present super low values in some indexes.

##### Factors

###### US

```{r}

#Initial tests
KMO(data_us_net)
cortest.bartlett(data_us_net)

#Number of factors

# #FA
# ev_us <- eigen(cor(data_us_net))
# ev_us$values
# scree(data_us_net) 
# 
# #PC
# pc_us = princomp(data_us_net)
# screeplot(pc_us) 

#Both
fa.parallel(data_us_net)

#FA
# fit_us5_fa <- factanal(data_us_net, factors=5, rotation = "varimax")
# fit_us5_fa

#EFA
fit_us5_efa = efa(data_us_net, nfactors = 5, rotation = "oblimin")
summary(fit_us5_efa, nd = 3L, cutoff = 0.2, dot.cutoff = 0.0)


```


```{r echo=TRUE}

#Indexes
data_us = data_us %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, b_equality))),
           index_2 = rowMeans(across(c(p_poor, p_black, b_diversity))),
           index_3 = rowMeans(across(c(ib_weafam, ib_edupar, ib_people))),
           index_4 = rowMeans(across(c(ib_edu, ib_work))),
           index_5 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))


factor_us1 = data_us_net %>% 
  select(p_income, p_wealth, b_equality)

factor_us2 = data_us_net %>% 
  select(p_poor, p_black, b_diversity)

factor_us3 = data_us_net %>% 
  select(ib_weafam, ib_edupar, ib_people)

factor_us4 = data_us_net %>% 
  select(ib_edu, ib_work)

factor_us5 = data_us_net %>% 
  select(ib_race, ib_migra, ib_relig, ib_sex)


#Cronbach
cronbach.alpha(factor_us1, CI=TRUE, standardized=TRUE) # 0.859
cronbach.alpha(factor_us2, CI=TRUE, standardized=TRUE) # 0.709
cronbach.alpha(factor_us3, CI=TRUE, standardized=TRUE) # 0.698
cronbach.alpha(factor_us4, CI=TRUE, standardized=TRUE) # 0.430
cronbach.alpha(factor_us5, CI=TRUE, standardized=TRUE) # 0.735

```


###### NL

```{r}

#Initial tests
KMO(data_nl_net)
cortest.bartlett(data_nl_net)

#Number of factors

# #FA
# ev_nl <- eigen(cor(data_nl_net))
# ev_nl$values
# scree(data_nl_net) 
# 
# #PC
# pc_nl = princomp(data_nl_net)
# screeplot(pc_nl) 

#Both
fa.parallel(data_nl_net)

#FA
# fit_nl5_fa <- factanal(data_nl_net, factors=4, rotation = "varimax")
# fit_nl5_fa

#EFA
fit_nl4_efa = efa(data_nl_net, nfactors = 4, rotation = "oblimin")
summary(fit_nl4_efa, nd = 3L, cutoff = 0.2, dot.cutoff = 0.0)


```

```{r echo=TRUE}

#Indexes
data_nl = data_nl %>% 
    mutate(index_1 = rowMeans(across(c(p_income, p_wealth, b_merit, b_equality))),
           index_2 = rowMeans(across(c(p_poor, p_black, b_diversity))),
           index_3 = rowMeans(across(c(ib_weafam, ib_edupar, ib_people, ib_edu, ib_work))),
           index_4 = rowMeans(across(c(ib_race, ib_migra, ib_relig, ib_sex))))


factor_nl1 = data_nl_net %>% 
  select(p_income, p_wealth, b_merit, b_equality)

factor_nl2 = data_nl_net %>% 
  select(p_poor, p_black, b_diversity)

factor_nl3 = data_nl_net %>% 
  select(ib_weafam, ib_edupar, ib_people, ib_edu, ib_work)

factor_nl4 = data_nl_net %>% 
  select(ib_race, ib_migra, ib_relig, ib_sex)

#Cronbach
cronbach.alpha(factor_nl1, CI=TRUE, standardized=TRUE) # 0.166
cronbach.alpha(factor_nl2, CI=TRUE, standardized=TRUE) # 0.485
cronbach.alpha(factor_nl3, CI=TRUE, standardized=TRUE) # 0.713
cronbach.alpha(factor_nl4, CI=TRUE, standardized=TRUE) # 0.816

```


##### Regression


```{r}
#Regression
m1_us_r = lm(att_redist ~ cca, data = data_us)
m2_us_r = lm(att_redist ~ index_1 + index_2 + index_3 + index_4 + index_5, data = data_us)
m3_us_r = lm(att_redist ~ cca + index_1 + index_2 + index_3 + index_4 + index_5, data = data_us)
m4_us_r = lm(att_redist ~ cca + index_1 + index_2 + index_3 + index_4 + index_5 + 
             age + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_us)

```

```{r}
#Regression
m1_nl_r = lm(att_redist ~ cca, data = data_nl)
m2_nl_r = lm(att_redist ~ index_1 + index_2 + index_3 + index_4 , data = data_nl)
m3_nl_r = lm(att_redist ~ cca + index_1 + index_2 + index_3 + index_4, data = data_nl)
m4_nl_r = lm(att_redist ~ cca + index_1 + index_2 + index_3 + index_4 + 
             age + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_nl)

```

```{r}

#Output
tab_model(list(m1_us_r, m2_us_r, m3_us_r, m4_us_r, m1_nl_r, m2_nl_r, m3_nl_r, m4_nl_r),
          #order.terms = c(1:5, 23, 6:22),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1-US", "M2-US", "M3-US", "M4-US", "M1-NL", "M2-NL", "M3-NL", "M4-NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on attitude towards redistribution - US & NL",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Article", "Tables", "Attitude_Redistribution_B.html")
)

```


#### Design C: All variables included

Third route: we can attempt to run a regression with all the CCA variables (inequality beliefs + perceptions + beliefs). This route avoids problems related to the indexes, but is probably hampered by collinearity arising between CCA items. If we do this we have a non significant CCA coefficient, and adding CCA do not increase the R2 of the model.

```{r}
#Regression
m1_us_ra = lm(att_redist ~ cca, data = data_us)
m2_us_ra = lm(att_redist ~ p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people  + ib_race +  ib_migra  + ib_relig + ib_sex, data = data_us)
m3_us_ra = lm(att_redist ~ cca + p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people +  ib_race +  ib_migra  + ib_relig + ib_sex, data = data_us)
m4_us_ra = lm(att_redist ~ cca + p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people  + ib_race +  ib_migra  + ib_relig + ib_sex + 
             age + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_us)

```

```{r}
#Regression
m1_nl_ra = lm(att_redist ~ cca, data = data_nl)
m2_nl_ra = lm(att_redist ~ p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people  + ib_race +  ib_migra  + ib_relig + ib_sex , data = data_nl)
m3_nl_ra = lm(att_redist ~ cca + p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people  + ib_race +  ib_migra  + ib_relig + ib_sex, data = data_nl)
m4_nl_ra = lm(att_redist ~ cca + p_income + p_wealth + p_poor +   p_black +  b_merit +  b_diversity + b_equality + ib_weafam  + ib_edupar  + ib_edu +   ib_work +  ib_people  + ib_race +  ib_migra  + ib_relig + ib_sex + 
             age + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = data_nl)

```

```{r}

#Output
tab_model(list(m1_us_ra, m2_us_ra, m3_us_ra, m4_us_ra, m1_nl_ra, m2_nl_ra, m3_nl_ra, m4_nl_ra),
          #order.terms = c(1:5, 23, 6:22),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1-US", "M2-US", "M3-US", "M4-US", "M1-NL", "M2-NL", "M3-NL", "M4-NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on attitude towards redistribution - US & NL",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Article", "Tables", "Attitude_Redistribution_C.html")
)

```

