---
title: "Design 1: Inequality Belief Systems and Attitude Towards Redistribution in US and the Netherlands"
author: ""
#date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  prettydoc::html_pretty:
    theme: architect
    fig_caption: yes
    df_print: paged
---

<style>
body {
text-align: justify}
</style>

```{r Setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	echo = FALSE,
	fig.align="center",
	out.width='\\textwidth'
	)
```

```{r include=FALSE}
library(pacman)
p_load(tidyverse, here, stargazer, sjmisc, texreg, sjPlot, jtools, kableExtra,
       poLCA, corclass, EGAnet, sjlabelled, haven, conflicted, DataExplorer,
       glue)
#imager

```


```{r}
rm(list = ls())

#Data
load(here("Output", "Design 1", "230314 - Output.RData"))

```


```{r}
#Packages conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
conflict_prefer("texreg", "extract")
conflict_prefer("sjlabelled", "get_label")
#conflict_prefer("labelled", "to_character")

options(max.print=999999)
options(scipen=999999)
```

# Design 1 

## Analysis structure

- CCA (perceptions and beliefs about inequality; without preference for redistribution) 
- EGA: CCA group 1 vs CCA group 2 (by country)
- Regression: sociodem -> CCA groups
- Factor analysis
- Histogram of preference for redistribution by CCA groups
- Regression: CCA groups + factors + controls -> preference for redistribution

# Variables

```{r}
mijs_us = mijs_us %>% 
  mutate(CCA = as.numeric(paste0(CCA)))

mijs_nl = mijs_nl %>% 
  mutate(CCA = as.numeric(paste0(CCA)))

```

```{r}
labels_data = sjlabelled::get_label(mijs_us) %>%
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  `colnames<-`(c("variable", "label")) %>% 
  slice(19:35)

labels_data %>% 
  kable()
  
```


## Descriptives

### US

```{r, results = "asis"}
#US
mijs_skim  = mijs_us %>% 
  
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "html")
```

### NL

```{r}
#NL
mijs_nl_skim  = mijs_nl %>% 
  mutate_if(is.character, as.numeric) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  as.data.frame() %>% 
  stargazer(type = "text")
```

# Inequality Belief Systems

## Distribution

### US

```{r}
frq(mijs_us, CCA)
```

### NL

```{r}
frq(mijs_nl, CCA)
```

## EGA

```{r, fig.height = 20}

#Rename data ega objects
data_ega_us1 = US_ega_CCA1
data_ega_us2 = US_ega_CCA2
data_ega_nl1 = NL_ega_CCA1
data_ega_nl2 = NL_ega_CCA2

#EGA list
data_egas <- lapply(ls(pattern="^data_ega_"), function(x) get(x))
data_egas <- data_egas[c(3,4,1,2)]

cca_groups = c("US_0", "US_1", "NL_0", "NL_1")

#Compare EGAs
comp_egas = compare.EGA.plots(
  input.list = data_egas,
  base.plot = 1,
  labels = cca_groups,
  rows = 4, columns = 1,
  plot.args = list(
    #vsize = 2, label.size = 2, edge.size = 0.2,
    legend.position = "none", legend.size = NA))

```

# Sociodemographic Determinants of Inequality Belief Systems

```{r}

# frq(mijs_us, age, agegroups, sex, race, education,
#          working, politics, pol5, 
#          hhincome, hhincome_groups, assets, immigrant, marital, religion, ladder_present)

#regression
m1_US = glm(CCA ~ politics, data = mijs_us, family=binomial(link="logit"))
m2_US = glm(CCA ~ politics + agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us, family=binomial(link="logit"))
m3_US = glm(CCA ~ agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us, family=binomial(link="logit"))

#xtable
#screenreg(list(m1_US, m2_US, m3_US), stars = c(0.01,0.05,0.1))
# tab_model(list(m1_US, m2_US, m3_US),
#           show.p = TRUE,
#           p.style = "stars",
#           p.threshold = c(0.1, 0.05, 0.01),
#           dv.labels = c("M1", "M2", "M3"),
#           collapse.ci = TRUE,
#           show.aic = TRUE,
#           #show.reflvl = TRUE,
#           title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - US",
#             string.pred = " "
# )
```

```{r}
#regression
m1_NL = glm(CCA ~ politics, data = mijs_nl, family=binomial(link="logit"))
m2_NL = glm(CCA ~ politics + agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl, family=binomial(link="logit"))
m3_NL = glm(CCA ~ agegroups + sex + race + education + working + assets + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl, family=binomial(link="logit"))

#xtable
#screenreg(list(m1_NL, m2_NL, m3_NL), stars = c(0.01,0.05,0.1))
# tab_model(list(m1_NL, m2_NL, m3_NL),
#           show.p = TRUE,
#           p.style = "stars",
#           p.threshold = c(0.1, 0.05, 0.01),
#           dv.labels = c("M1", "M2", "M3"),
#           collapse.ci = TRUE,
#           show.aic = TRUE,
#           #show.reflvl = TRUE,
#           title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - NL",
#             string.pred = " "
# )
```

```{r}
tab_model(list(m1_US, m2_US, m3_US, m1_NL, m2_NL, m3_NL),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M1_US", "M2_US", "M3_US", "M1_NL", "M2_NL", "M3_NL"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Logistic regression models on the probability to be a member of the CCA group 1 (CCA) - US & NL (Full sample)",
            string.pred = " "
)
```

# Inequality Belief Systems and Attitude Towards Redistribution

## Factor analysis

```{r}
#EGA US
mijs_us_net = mijs_us %>% 
  select(perc_income:ib_sex)

US_ega = EGA(data=mijs_us_net,  model = "TMFG", 
                  plot.EGA = TRUE) 

#EGA NL
mijs_nl_net = mijs_nl %>% 
  select(perc_income:ib_sex)

NL_ega = EGA(data=mijs_nl_net,  model = "TMFG", 
                  plot.EGA = TRUE) 

#CFA
data_cfa_us = CFA(US_ega, mijs_us_net, estimator = "WLSMV")
data_cfa_nl = CFA(NL_ega, mijs_nl_net, estimator = "WLSMV")


#indexes
mijs_us = mijs_us %>% 
    mutate(index_1 = rowMeans(across(c(perc_income:perc_black, bel_diversity, bel_equality))),
           index_2 = rowMeans(across(c(bel_merit, ib_work, ib_race:ib_sex))),
           index_3 = rowMeans(across(c(ib_weafam:ib_edu, ib_people))))


mijs_nl = mijs_nl %>% 
    mutate(index_1 = rowMeans(across(c(perc_income:bel_equality))),
           index_2 = rowMeans(across(c(ib_race:ib_sex))),
           index_3 = rowMeans(across(c(ib_weafam:ib_people))))
```
**We use EGA on the full sample to:** 

1. Fit CFA (EGA communities = factors)
2. Obtain fit 
3. Create indexes


## Graphs

### US

```{r}
#graph
mijs_us_n = nrow(mijs_us)

crosstab_US = mijs_us %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_US.jpg"), plot =  crosstab_US)

crosstab_US
```

### NL

```{r}
#graph
mijs_nl_n = nrow(mijs_nl)

crosstab_NL = mijs_nl %>%
  group_by(CCA) %>% 
  mutate(n_cca = n()) %>%
  group_by(CCA, att_redist) %>% 
  summarise(count = n(),
           pct = count / n_cca) %>% 
  slice(1) %>% 
  ggplot(aes(y=pct, x=att_redist)) +
  geom_col() +
  facet_wrap(~CCA) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:7) +
  labs(x="Attitude towards redistribution", y="Percentage")
ggsave(filename = here("Output", "graph_tab_NL.jpg"), plot =  crosstab_NL)

crosstab_NL

```
## Regressions


```{r}
#regression us
m0_US = lm(att_redist ~ index_1 + index_2 + index_3, data = mijs_us)
m1_US = lm(att_redist ~ CCA, data = mijs_us)
m2_US = lm(att_redist ~ index_1 + index_2 + index_3 + CCA, data = mijs_us)
m3_US = lm(att_redist ~ index_1 + index_2 + index_3 + CCA + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_us)

# NL
m0_NL = lm(att_redist ~ index_1 + index_2 + index_3, data = mijs_nl)
m1_NL = lm(att_redist ~ CCA, data = mijs_nl)
m2_NL = lm(att_redist ~ index_1 + index_2 + index_3 + CCA, data = mijs_nl)
m3_NL = lm(att_redist ~ index_1 + index_2 + index_3 + CCA + agegroups + sex + race + education + working + politics + 
        hhincome_groups + immigrant + marital + religion, data = mijs_nl)
```

### US

```{r}
tab_model(list(m0_US, m1_US, m2_US, m3_US),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M0", "M1", "M2", "M3"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on preference for redistribution - US",
            string.pred = " "
)
```


### NL

```{r}
tab_model(list(m0_NL, m1_NL, m2_NL, m3_NL),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("M0", "M1", "M2", "M3"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          #show.reflvl = TRUE,
          title = "Table. Linear regression models on preference for redistribution - NL",
            string.pred = " "
)
```



        